---
title: "OCTGN ID Loyalty Analysis"
author: "Ajar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OCTGN ID Loyalty Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

## Introduction



## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
library(netrunner)

octgn <- read.octgn("~/Downloads/OCTGN_stats_anonymized-2015-02-20.csv")

ratings <- rate.players(octgn)
sig1 <- prune.players(ratings, min.rating = mean(ratings$Rating, na.rm = TRUE) + sd(ratings$Rating, na.rm = TRUE), max.deviation = 200, min.games = 5)
sig1.games <- prune.games(octgn, sig1$Player)


loyal.corp <- octgn.game10 %>% 
  inner_join(., ratings[, 1:2], by = c("Runner_Player" = "Player")) %>%
  group_by(Corp_Player, Corporation) %>%
  summarise(Games = n(), 
            Winrate = sum(Win, na.rm = TRUE) / Games,
            Opp_Rating = mean(Rating)) %>%
  mutate(Loyalty =  Games[which.max(Games)] / sum(Games, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(Corp_Player) %>%
  summarise(Games = sum(Games), 
            Winrate = floor(mean(Winrate * Games)) / Games,
            Loyalty = mean(Loyalty),
            Opp_Rating = mean(Opp_Rating)) %>%
  filter(Games > 20)

ggplot(loyal.corp, aes(Loyalty, Winrate)) +
  geom_point(aes(color = loyal.corp$Opp_Rating, alpha = 0.4)) +
#   scale_colour_gradient2(low = muted("red"), high = muted("blue")) + 
  xlab("Corp Loyalty") +
  ylab("Corp Winrate")
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

```{r, fig.show='hold'}

library(netrunner)

octgn <- read.octgn("~/Dropbox/Personal/Netrunner/OCTGN_stats_anonymized-2014-08-25.csv")

octgn$Period <- floor_date(octgn$GameStart, "month")

octgn$Period %<>% cut(breaks = "month") %>% as.numeric()

results <- list()
plots <- list()
  
for ( i in seq_along(unique(octgn$Period)) ) {

  games <- filter(octgn, Period == i)
  
  ratings <- octgn %>% 
#     group_by(Period) %>%
    mutate(Win = as.numeric(Win)) %>%
    select(Period, Corp_Player, Runner_Player, Win) %>%
    glicko(history = FALSE, sort = TRUE, init = c(1500, 350))
  
  sig1 <- prune.players(ratings$ratings, min.rating = min(ratings$ratings$Rating, na.rm = TRUE), max.deviation = 200, min.games = 5)
  sig1.games <- prune.games(games, sig1$Player)


  loyal.corp <- sig1.games %>% 
    inner_join(., ratings$ratings[, 1:2], by = c("Runner_Player" = "Player")) %>%
    group_by(Corp_Player, Corporation) %>%
    summarise(Games = n(), 
              Winrate = sum(Win, na.rm = TRUE) / Games,
              Opp_Rating = mean(Rating)) %>%
    mutate(Loyalty =  Games[which.max(Games)] / sum(Games, na.rm = TRUE)) %>%
    ungroup() %>%
    group_by(Corp_Player) %>%
    summarise(Games = sum(Games), 
              Winrate = floor(mean(Winrate * Games)) / Games,
              Loyalty = mean(Loyalty),
              Opp_Rating = mean(Opp_Rating)) %>%
    filter(Games > 20)

  ggplot(loyal.corp, aes(Loyalty, Winrate)) +
    geom_point(aes(color = loyal.corp$Opp_Rating, alpha = 0.4)) +
  #   scale_colour_gradient2(low = muted("red"), high = muted("blue")) + 
    xlab("Corp Loyalty") +
    ylab("Corp Winrate")
  
  ggsave(filename = paste0("~/Dropbox/Personal/Netrunner/package/plots/loyalty_period_", i, ".png"))

  results[[i]] <- loyal.corp
  
}

```

Looks like no aggregate effect even within smaller periods. Next question is whether someone who is initially not loyal has more success in periods where they are loyal. 

```{r, fig.show='hold'}

library(netrunner)
library(lubridate)

octgn <- read.octgn("~/Downloads/OCTGN_stats_anonymized-2015-02-20.csv", 
                    id.rm = c('Shaper | The Collective', 'Criminal | Laramy Fisk'))

octgn$Period <- floor_date(octgn$GameStart, "month")

octgn$Period %<>% cut(breaks = "month") %>% as.numeric()

ratings <- rate.players(octgn, history = TRUE, period.select = "month")

min5 <- prune.players(ratings$ratings, 
                      min.rating = min(ratings$ratings$Rating, na.rm = TRUE), 
                      max.deviation = 200,
                      min.games = 5)

octgn <- prune.games(octgn, players = min5$Player, keep = TRUE)

ratings <- rate.players(octgn, history = TRUE, period.select = "month")


lag.rating <- function(id, Period) { as.list(ratings$history[which(ratings$ratings$Player == id), Period, 1]) }

ids <- unique(ratings$ratings$Player)

lags <- lapply(ids, FUN = lag.rating, Period = c(1:26))

lags <- rbindlist(lags)

lags$Player <- ids

lags <- as.data.frame(lags)

lags <- lags[c("Player", as.character(1:26))]

octgn %<>% inner_join(., lags, by = c("Corp_Player" = "Player"))

# octgn %<>% inner_join(., lags, by = c("Runner_Player" = "Player"))

cl <- octgn %>%
  tbl_df() %>%
  group_by(Period, Corp_Player, Corp_Faction) %>%
  mutate(Games = n()) %>%
  ungroup() %>%
  group_by(Period, Corp_Player) %>%
  mutate(Loyalty = Games[which.max(Games)] / n()) %>%
  filter(Games > 10)

for ( i in 2 : (length(unique(octgn$Period)) - 1) ) {

  data <- filter(cl, Period == i)
  
  data$delta <- data[, i + 24] - data[, i + 23]

  message(cor(data$Loyalty, data$delta))
  
  ggplot(data, aes_string(x = "Loyalty", y = paste0("`", i + 1, "`"))) +
    geom_point() +
    xlab("Corp Loyalty in Period X") +
    ylab("Corp Rating in Period X + 1")

  ggsave(filename = paste0("~/Dropbox/Personal/Netrunner/package/plots/corp_loyalty_delta_", i, ".png"))
  
  # Next, plot loyalty vs games played to see if loyal people play more (or the reverse)
  # Plot loyalty vs change in rating from period X to period X + 1
  
  
  
}
  
```

